---
title: "EDA_on_diamonds_dataset"
author: "Ayobami Alaran"
date: '2022-06-26'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Exploratory Data Analysis on Diamond dataset

## Importing the libraries
```{r}
library(tidyverse)
library(ggplot2)
```

### Assessing the dataset
head functions shows the top 6 rows of the set
```{r}
head(diamonds)
```

```{r}
str(diamonds)
```

```{r}
glimpse(diamonds)
```

Lets check the column names 
```{r}
colnames(diamonds)
```

### Cleaning the data

Renaming the color column name to colour
```{r}
rename(diamonds, colour=color)
```

## Exploratory data analysis

What is the average carat of the diamond
```{r}
summarise(diamonds, avg_carat=mean(carat)) 
```

## Data Visualization
showing the relationship between the diamond carat and price 
```{r}
ggplot(data = diamonds, ) +
  geom_point(mapping=aes(x = carat, y = price))
```
```{r}
cor(select(diamonds, carat, price))
```
## Interpretation 
from the data viz result, we can see that there is an upward movement in the trend that is there is a relationship between the the two variables, the bigger the carat the higher the price. 
for further investigation, the correlation shows that there is 0.92 correlation between the carat and price.

```{r}
ggplot(data = diamonds, aes(x = carat, y = price, color = cut)) +
  geom_point()
```




